\section{Physics of NLS}
Physics - Chapter 1
NLS as leading-order model for propagation of intense laser beams in isotropic bulk medium. A laser pulse is an electromagnetic wave and is governed by Maxwell’s equations.
Deriving the wave equation from Maxwell is a classic result: Lemma 1.1.
Each component of the electric field satisfies a scalar wave equation and has plane waves as solution with certain dispersion relation. More generally, these plane waves are expressed … with c.c. the complex conjugate.
Linear polarisation of a plane wave. Actually, laser pulse is not linearly polarised, but the leading-order approximation of the laser pulse is linearly polarised.
Now laser beams are (time harmonic) continuous wave solutions to the scalar wave equation. And these yield the scalar linear Helmholtz equation. Plane waves are solutions to a specific scalar linear Helmholtz equation.
Laser beam propagating in $z$-direction, $E_0^inc$ known at $z=0$. Unlike the plane wave, the laser beam electric field decays to zero as the distance from the beam axis goes to infinity. Nevertheless, it can be expressed as a linear superposition of plane waves: and has a corresponding right-propagating solution that is a solution to the Helmholtz equation (each mode is a plane wave, equal to $E_0^inc$ at $z=0$ and propagating in positive $z$-direction. Most of the modes travel parallel to the $z$-axis and are called paraxial plane waves that satisfy .... The favoured solutions to the Helmholtz equation are travelling in the $z$-direction and have electric field envelope that has its own Helmholtz equation with a diffraction term. For example, plane waves can be expressed ... and have an envelope slowly varying as a function of $z$, compared to the carrier oscillations. Lemma 1.2

If the paraxial laser beam mostly consists of paraxial plane waves, suggesting to neglect the ... , and this paraxial approximation yields a linear Schrödinger equation for the envelope. Worth noting: this is a SE arising from classical physics. Also: neglecting the highest-order derivative changes the problem from a boundary problem (Helmholtz) to an initial value problem (Schrödinger). Nevertheless, the results of the approximation agree with experiments. When the electric field is applied to a dielectric medium it induces an additional electric field called polarisation field. There are three mechanisms contributing. To simplify, the electric field is assumed to be linearly polarised and continuous wave, and the dielectric medium is isotropic and homogenous. 

LINEAR, WEAKLY NONLINEAR, KERR NONLINEAR, VECTORIAL KERR NONLINEAR, WEAKLY NONLINEAR HELMHOLTZ, NONLINEAR SCHRODINGER, RELATIVE MAGNITUDE OF KERR, VALIDITY OF NLS.



Chapter 2
Laser beams in a Kerr medium can become narrower with propagation (self-focusing) and is studies through geometric approximation. Start with the dimensional linear Helmholtz equation. Geometric approximation is valid when changes occur over distances much greater than the wavelength, so locally the medium is homogenous. Then create the dimensionless linear Helmholtz. There is the Eikonal equation. This is a nonlinear first-order PDE. The rays (...) are determined by the system of six linear ODEs. Lemma 2.1 states that under the geometric approximation, the rays of the Eikonal equation are perpendicular to the wavefronts of the Helmholtz equation. Fermats principle of least time was refined to the principle of stationary time. Rays connecting two points are extremals of the Traveltime functional. (Geometric approximation -- ray description of light propagation.) Transport equation implies that the power of a ray bundle at a cross-section is constant. This implies that a focused beam has all beam power in a focal point.

\begin{enumerate}
\item PARAGRAPH 2 IS MANY APPLICATIONS, ALSO WAVEGUIDES.
\item PARAGRAPH 3 IS COLLIMATED BEAMS.
\item PARAGRAPH 4 IS FUNDAMENTAL SOLUTION TO HELMHOLTZ.
\item PARAGRAPH 5 IS HELMHOLTZ FOCUSED BEAMS.
\item PARAGRAPH 6 IS SINGULARITY IN HELMHOLTZ.
\item PARAGRAPH 7 IS GLOBAL EXISTENCE IN THE LINEAR HELMHOLTZ.
\item PARAGRAPH 8 IS REPRESENTATION OF INPUT BEAMS.
\item PARAGRAPH 9 IS GEOMETRICAL ANALYSIS OF PARAXIAL PROPAGATION.
\item PARAGRAPH 10 IS ARREST OF LINEAR COLLAPSE BY DIFFRACTION (GAUSSIAN).
\item PARAGRAPH 11 IS DIFFRACTION LENGTH.
\item PARAGRAPH 12 IS DIMENSIONLESS LINEAR SCHRODINGER.
\item PARAGRAPH 13 IS FOURIER TRANSFORM.
\item PARAGRAPH 14 IS NORMS.
\item PARAGRAPH 15 IS LINEAR SCHRODINGER ANALYSIS.
\item PARAGRAPH 16 IS NON-DIRECTIONALITY.
\item PARAGRAPH 17 IS LINEAR AND NONLINEAR SINGULARITIES.
\end{enumerate}

Chapter 3
Early Self-Focusing Research (Include 3.1, 3.2, 3.3, 3.4, Omit 3.5 and 3.6 and Include 3.7)
