\section{Introduction}
% In this chapter, we study the paper "Uniqueness of the Ground State Solution for
% $\Delta u - u + u^3 = 0$ and a Variational Characterization of Other Solutions"
% written in 1972 by Charles V. Coffman. 

\todo{Make connection to chapter 2 and discuss similarities and differences.
Berestycki shows existence for $f(u)$ satisfying certain conditions, the problem
considered here is the specific case for $f(u) = u - u^3$. 

Existence in this paper was based on Nehari/Ryder/Berger. They show existence
for a smaller (?) family of $f(u)$. Nehari: $f(u) = u - u^k$ with $1<k\leq 4$.
Ryder more general: $\Delta u = u - u f(u^2)$. Berger: $i\frac{\partial
u}{\partial t} = \Delta u + f(|x|, |u|^2)u$ under the assumption that $f(|x|,
|u|^2)=k(|x|)|u|^\sigma$ for $0<\sigma<4$ and $k(|x|)$ a Lipschitz continuous
positive bounded function.}

In this chapter, we study a paper from 1972 by Charles V. Coffman \cite{coffm}. 
The paper proves uniqueness of the positive radially symmetric (ground
state) solution $u=\phi_1\in C^2\cap L^4$ for the equation
\be\label{upde}
\Delta u - u + u^3 = 0\quad\text{in }\R^3.
\ee

Note that all function spaces consist of real valued functions on $\R^3$.
Furthermore, radial symmetry is with respect to the origin only. 

The existence of such a function $\phi_1$ was shown in \cite{nehari},
where $\phi_1=v_1(|x|)$ solves \eqref{upde}. In fact, there exist functions
$v_n(|x|)\in C^2([0, \infty))$, $n=1, 2, \ldots$, such that for each $n$, $v_n$
has exacly $n-1$ isolated zeroes in $[0, \infty)$, decays exponentially as
$r\to\infty$. This was shown in \cite{ryder, berger}

Moreover, Theorem 3.1 of \cite{coffm} improves the result of \cite{robinson}, 
which also studied \eqref{upde} (in the context of variational calculus). 
In \cite{robinson}, they show that the Lagrangian associated with \eqref{upde}
is zero in its first variation and the second variation is positive if
$\lambda_1 > 1$. The latter is shown only through approximations. Theorem 3.1 of
\cite{coffm} shows that the Rayleigh quotient $J$ associated with \eqref{upde}
\be\label{rayleigh} 
J(u) = \dfrac{\left(\int\left|\nabla u\right|^2+u^2~dx\right)^2}{\int u^4~dx}
\ee

is indeed minimal for %$u=\phi_1$ and for 
\be\label{uts}
u(x)=k\phi_1(x+x_0),\quad\text{where}~k\neq0~\text{and}~x_0\in\R^3
\ee
% for any $k\neq 0$ and $x_0\in \R^3$. 
The right hand side of \eqref{rayleigh} is
meaningful for admissible functions. \todo{Fit definition on same page?}

\begin{definition} 
    A function $u$ is \emph{admissible} if $u\in H^1$ and $u\neq 0$.
\end{definition}
